### 2021-06-29 README.Rmd
Modify readme to reflect repository contents for completed manuscript

The goal of pvdiv-phenology-gxe is to analyze the genetics of GxE in the phenology data collected for the switchgrass diversity panel in 2018 and 2019, including tiller count in 2018, survival to 2019, and greenup to tiller count & biomass in 2019. This repository will be private until the associated dataset is published.

As of December 2019, this analysis is on data Jason Bonette compiled 2019-12-25. I create downstream data objects from data collected on this date. At the beginning of every month, and whenever I hear from him, I will check his dataset for any changes.

R Files:

In data-raw/:

@@

>>>>

pvdiv-phenology-gxe contains the non-genomic data and code used to analyze the genetics of GxE in the phenology data collected for the switchgrass diversity panel in 2019, including green-up dates and flowering dates in 2019. This repository will be private until the associated manuscript is published.

In general, if you have any questions about how to locate an analysis folder or code used for an analysis, look at this README first. Then, if you still have questions, feel free to open a pull request with your issue and I will be happy to help.

## Repository Files:

### In data-raw/:

@@

### In data/:

    * Contains datasets as ".rds" files that are used in analyses (to produce results in the analysis/ folder). These files can be read into R using the `readRDS()` function.

### In analysis/:

    * Data objects and draft figures created as part of the analysis of heritability (including variance components analysis, done in ASReml), genome-wide association (on phenotypic BLUPs, done using the switchgrassGWAS R package), and mash (on results from the univariate GWAS, done using the switchgrassGWAS R package). Generally, the code to replicate these analyses can be found in the R/ directory.

### In R/:

    * Contains the majority of the code used in the manuscript (some additional code used to prepare data is in data-raw/.) 
    * Files that start with "Plots" were used to make manuscript figures
    * Files that start with "nohup" were used to run mash
    * Files that start with "Analysis" were used to generate files in the analysis/ folder. I tried to name these descriptively but there are a lot of them; please open a pull request if you want help locating specific code.

### In phenology-fourway/:

    * Code and data objects needed to replicate the genetic mapping of flowering-related QTL in the pseudo-F2 cross.

### In manuscript/:

    * Contains completed drafts of a manuscript on the genetics of GxE in phenology in the switchgrass diversity panel.
